Distributed Version Control Systems

### 2010-05-16 paper.tex
Re-escritura de Architecture basado en 'no comparar' con svn

% format author this way for journal articles.
% MAKE SURE THERE ARE NO SPACES BEFORE A \member OR \authorinfo
% COMMAND (this also means `don't break the line before these
% commands).
\author[GRUPOAPIT]{Demian Alonso,
\and{} Bruno Bonnano,
\and{} Nicol\'{a}s Calligaro
\and{}and Nicol\'{a}s Perez Santoro
}

@@

@@

\section{Possible workflows}

@@

Then both repositories can be merged togheter into an integration one by pulling from each of them. If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved. Then this team can clone the integration repository and merge it with its working repository. They can ask the person in charge to pull the changes back again.

\subsection{Centralized repository with integration manager}
It is possible to have a single central repository where all developers have read access. Everyone has an official public version from which they can work from. Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed. When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.

@@

>>>>

% format author this way for journal articles.
% MAKE SURE THERE ARE NO SPACES BEFORE A \member OR \authorinfo
% COMMAND (this also means `don't break the line before these
% commands).
\author[GRUPOAPIT]{Damian Alonso,
\and{} Bruno Bonnano,
\and{} Nicol\'{a}s Calligaro
\and{}and Nicol\'{a}s Perez Santoro
}

@@

A DVCS has many features that makes it perfect for distributed and non-distributed developments. Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools and relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.

\subsection{Distributed}
The idea behind being distributed means that no server has the full content of a repository but rather a clone of it with the changes that a particular developer has commited. This allows users to have their own clone on their own computer and work in a offline environment while being able to version their changes. It also makes the whole versioning system faster.

\subsection{Change-sets}
You could also create several other clones for every feature or bug that they want to develop and push those changes to another clone, a co-worker's repository for instance, and pull some changes from another co-worker to your local clone. To able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.

\subsection{Patchs}
The idea of having several clones, one for each feature or bug might be problematic so instead of doing that, you could have all your changes on a single clone and then select which one of those changes you want to commit. You can even select which parts of a single file you want to commit and which ones you don't, then group those changes and commit them in a very atomic way.

\subsection{Flexibility}
If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository. This shows how flexible a DVCS is, to the point of being able to describe it as a super-set of a centralized CVS although in really it is not.

\subsection {Distributed Repository}

@@

\section{Should I use it in my project?}

@@

Then both repositories can be merged togheter into an integration one by pulling from each of them. If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved. Then this team con clone the integration repository and merge it with its working repository. They can ask the person in charge to pull the changes back again.

@@

%----------------------------------------------------------------------
\section{Glossary}
{\renewcommand{\labelitemi}{$\triangleright$}
\begin{itemize}
\item CVS
\item Centralized CVS
\item Distributed/de-centralized CVS
\end{itemize}
